---
title: "ML Linear Regression Project"
author: "Ankita Hanmiah"
date: "February 28, 2019"
output: pdf_document
---

states.data <- readRDS("dataSets/states.rds")

###Exercise 1: Least Squares Regression

## Use the /states.rds/ data set. Fit a model predicting energy consumed per capita (energy) from the percentage of residents living in metropolitan areas (metro). Be sure to:

##   1. Examine/plot the data before fitting the model
##   2. Print and interpret the model `summary'
##   3. `plot' the model to look for deviations from modeling assumptions

```{r}
met.energy <- subset(na.omit(states.data), select = c("metro", "energy"))
summary(met.energy)
plot(energy ~ metro, data = met.energy)
cor(x = met.energy$metro, y = met.energy$energy)
```
From the plot and looking at the correlation coefficient (which is -0.3117), we
can see that there is a negative relationship between residents living in metropolitan
areas and energy consumed per capita, and that it is not a strong relationship

```{r}
met.energy.lm <- lm(energy ~ metro, data = na.omit(states.data))
summary(met.energy.lm)
```
The negative relationship we expected based on the correlation coefficient is
supported by the negative coefficient in the linear regression model. We also
see with the above model that metro has slight significance in this model but
the R squared value is very low at 0.1154, which indicates that the data's fit to the 
line is not that strong.


##   Select one or more additional predictors to add to your model and
##   repeat steps 1-3. Is this model significantly better than the model
##   with /metro/ as the only predictor?

```{r}
summary(lm(energy ~ metro + green, data = na.omit(states.data)))
```
Adding the variable of greenhouse gas percentage showed a very significant relationship
between greenhouse gas and energy consumption, and though it did take the significance 
away from the relationship between energy consumption and percentage of metropolitan residents,
it raised the R squared value to 0.5939.
```{r}
summary(lm(energy ~ metro + green + toxic, data = states.data))
```

Adding another predictor of toxics released gives us high significance for greenhouse gas and 
toxics released, with still no significance for metropolitan area residents. The R squared value
jumped up to 0.7644 with the addition of this predictor.

###Exercise 2: Interactions and Factors

## Use the states data set.

##   1. Add on to the regression equation that you created in exercise 1 by
##      generating an interaction term and testing the interaction.
```{r}
energy.metro.green <- lm(energy ~ metro*green, data=states.data)
coef(summary(energy.metro.green))
```
The interaction term we created was metro*green and as seen by the p-value (.00036), the
interaction between metro and green is very significant.

##   2. Try adding region to the model. Are there significant differences
##      across the four regions?
```{r}
states.data$region <- factor(states.data$region)
metro.region <- lm(metro ~ region, data = states.data)
coef(summary(metro.region))
```
There are no significant differences across the northeast, midwest, and south. 